A robust framework for variable extrusion width concentric toolpath generation

### 2019-07-08 6_validation.tex
planning of example shapes

\subsection{Filling accuracy}
Render toolpaths and calculate percentage of covered volume.

Visualize thickness of beads as color.

@@

Also render with nozzle size as minimal width and use middle of toolpaths instead of middle of beads.

Take same examples as Moessen: grids of triangular holes and circular holes.
Also use examples of Jin and Kao.

Use example layers of a typical object with thin walls: electronics casing.

>>>>

\subsection{Filling accuracy}
Render toolpaths and calculate amount of overfilling and amount of underfilling.

\old{Visualize thickness of beads as color.}

@@

\old{Also render with nozzle size as minimal width and use middle of toolpaths instead of middle of beads.}

Example shapes:
\begin{itemize}
\item same as Moessen: grids of triangular holes
\item same as Moessen: circular holes.
\item same as Jin 
\item same as Kao
\item wedge
\item layer of a typical model: phone case
\item some of the above shapes, but with some fuzzy randomized outline
\end{itemize}
